---
title: "My Santa Barbara Study Spots"
format: html
categories: [Interactive Map]
---

Whenever I am sick of studying on campus at the Library or Bren Hall, I venture to our local Santa Barbara coffee shops in order to be productive and see a change of scenery out of Isla Vista. Below is an interactive map of some of my favorites that I frequent. 

## Interactive Map

```{r}
#| echo: false
#| message: false
#| warning: false

# loading in packages
library(sf)  # spatial data handling             
library(leaflet) # interactive map creation       
library(htmltools) # HTML rendering for labels and popups   
library(janitor) # cleaning column names
library(tidyverse) # data manipulation and piping
library(readr)  # reading CSV files
library(dplyr)


# reading in data 
ss <- read_csv("study_spots.csv")

# loading in icon 
studio_icon <- makeIcon(
  iconUrl = here::here("coffee.png"),
  iconWidth = 15, iconHeight = 20)
```

```{r}
#| echo: false
#| message: false
#| warning: false

# making map of studios 

site_map <- leaflet() |> 
  
  # add base map tiles (use `addTiles()` for Google maps tiles, OR `addProviderTiles()` for 3rd party base maps: https://leaflet-extras.github.io/leaflet-providers/preview/) ----
  addProviderTiles(providers$Esri.WorldImagery, group = "ESRI World Imagery") |>  
  addProviderTiles(providers$Esri.OceanBasemap, group = "ESRI Oceans") |> 
  
  # add mini map ----
  addMiniMap(toggleDisplay = TRUE, minimized = TRUE) |> 
  
  # set view over Goleta + SB ----
  setView(lng = -119.78, lat = 34.430, zoom = 12) |> 
  
  # add markers ----
  addMarkers(data = ss, group = "name", 
             icon = studio_icon,
             lng = ~long, lat = ~lat,
             popup = ~paste0(name, "<br>",
                             hours, "<br>",
    "Coordinates: ", lat, ", ", long
  )) |> 
  
   # add layers control (toggle base map tiles & markers based on group IDs) ----
  addLayersControl(
    baseGroups = c("ESRI World Imagery", "ESRI Oceans"),
    overlayGroups = c("name"))

  
#view map 
site_map
```

## My Orders 
Typically I usually order: 

- Cappuccino with almond or cocounut milk 

- Cold brew with a splash of coconut milk 

- Iced matcha with almond milk (+ lavendar syrup)

- Matcha lemonade

- Iced latte with coconut milk 


